---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tibble)
```

# stacking

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stacking)](https://CRAN.R-project.org/package=stacking)
<!-- badges: end -->

The goal of stacking is to provide a dataset that arose from a set of experiments intended to benchmark the time-to-fit and predictive performance of a number of alternative model stacking methods (or "meta-learners") for use in the stacks package.

## Installation

You can install the development version of stacking like so:

``` r
pak::pak("simonpcouch/stacking")
```

## Data

The dataset in the stacking package looks like this:

```{r example}
library(stacking)

stacking
```
